ARGoS-Blockchain interface

### 2020-09-04 article.tex
fastpush

\title{ARGoS-Blockchain interface}
\author{Volker Strobel \and Alex Pacheco \and Marco Dorigo}

@@

\begin{abstract}

  This technical report documents the installation and use of the
  ARGoS-Blockchain interface. This interface allows for conducting
  experiments in the robot swarm simulator ARGoS and the smart
  contract blockchain framework Ethereum. The blockchain part uses the
  container software Docker in order to facilitate the installation
  and the parallelization of the blockchain nodes. The use of
  blockchain-based smart contracts provides a framework for managing
  security issues in robot swarms. The interface is a convenient way
  to prototype blockchain-based control software in robot
  swarms. Byzantine robots, that is, robots that behave in an
  unintended way can disrupt the swarm behavior. In this technical
  report, we detail the motivation, setup, and usage of the
  ARGoS-blockchain interface.

@@

Several recent works have addressed the combination of blockchain
technology and swarm robotics
\cite{StrCasDor2018:aamas,StrDor2018:ants,StrFerDor2017:techreport-013}. This
combination proves useful for security, consensus finding, robot
economies, robot-as-a-service, and potentially many other applications
in robot swarms. However, conducting experiments involving robot
swarms and blockchain technology requires a suitable testbed. A widely
used framework consists of the Pi-puck robot platform running the
Ethereum blockchain network. However, not every researcher has access
to physical robots, obtaining and maintaining them be both
time-intense and cost-intense, not to mention the lengthy execution of
experiments. Therefore, a simulation testbed is needed to quickly try
and test different controllers and scenarios. The ARGoS robot
simulator \citep{PinTriOGr-etal2012:si} is the state-of-the-art
research platform to conduct simulations in swarm robotics. Such a
framework proves useful both for researchers who do not have access to
a suitable robot platform, such as the Pi-puck robot. Additionally, a
suitable platform is important before running time- and cost-consuming
experiments with real robots.

>>>>

\title{ARGoS-Blockchain interface}
\author{Volker Strobel \and Eduardo Castell\'o Ferrer \and Alex Pacheco \and Marco Dorigo}

@@

\begin{abstract}
  This technical report documents the installation and use of the
  ARGoS-Blockchain interface. This interface allows for conducting
  experiments in the robot swarm simulator ARGoS and the smart
  contract blockchain framework Ethereum. The blockchain part uses the
  container software Docker in order to facilitate the installation
  and the parallelization of the blockchain nodes. The use of
  blockchain-based smart contracts provides a framework for managing
  security issues in robot swarms. The interface is a convenient way
  to prototype blockchain-based control software in robot
  swarms. Byzantine robots, that is, robots that behave in an
  unintended way can disrupt the swarm behavior. In this technical
  report, we detail the motivation, setup, and usage of the
  ARGoS-blockchain interface.

@@

Several recent works have addressed the combination of blockchain
technology and swarm robotics
\cite{PacStrDor2020:techreport-007,StrCasDor2018:aamas,StrDor2018:ants,StrFerDor2017:techreport-013}. This
combination proves useful for security, consensus finding, robot
economies, robot-as-a-service, and potentially many other applications
in robot swarms. However, conducting experiments involving robot
swarms and blockchain technology requires a suitable testbed. A widely
used framework consists of the Pi-puck robot platform running the
Ethereum blockchain network. However, not every researcher has access
to physical robots, obtaining and maintaining them be both
time-intense and cost-intense, not to mention the lengthy execution of
experiments. Therefore, a simulation testbed is needed to quickly try
and test different controllers and scenarios. The ARGoS robot
simulator \citep{PinTriOGr-etal2012:si} is the state-of-the-art
research platform to conduct simulations in swarm robotics. Such a
framework proves useful both for researchers who do not have access to
a suitable robot platform, such as the Pi-puck robot. Additionally, a
suitable platform is important before running time-consuming
experiments with real robots.
